quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-19 paper-quollr.Rmd
Updated algorithm steps figure

scurve_umap_plt <- ggplot(
  scurve_umap_scaled, 
  aes(x = emb1, y = emb2)) +
  geom_point(alpha = 0.5, color = clr_choice, size = 0.5)

scurve_umap_plt_int <- ggplotly(scurve_umap_plt, 
                                width = "250", 
                                height = "250", 
                                tooltip = "none") |>
  config(
    staticPlot = TRUE,        # Disables all interactivity (no hover, zoom, pan)
    displayModeBar = FALSE,   # Hides the plotly toolbar
    editable = FALSE,         # Disables annotations and editing
    showTips = FALSE,         # Removes tooltip on hover
    displaylogo = FALSE,      # Hides plotly logo
    responsive = FALSE        # Disables responsive resizing
  )

hex_grid_poly_scurve <- ggplot(
  data = hex_grid_with_counts_scurve, 
  aes(x = x, y = y)) +
  geom_polygon(color = "grey70", 
               aes(group = hex_poly_id), 
               fill = "#ffffff") +
  geom_point(data = scurve_umap_scaled, 
             aes(x = emb1, y = emb2), 
             alpha = 0.2, size = 0.5, color = clr_choice)

hex_grid_poly_scurve_int <- ggplotly(hex_grid_poly_scurve, 
                                width = "250", 
                                height = "250", 
                                tooltip = "none") |>
  config(
    staticPlot = TRUE,        # Disables all interactivity (no hover, zoom, pan)
    displayModeBar = FALSE,   # Hides the plotly toolbar
    editable = FALSE,         # Disables annotations and editing
    showTips = FALSE,         # Removes tooltip on hover
    displaylogo = FALSE,      # Hides plotly logo
    responsive = FALSE        # Disables responsive resizing
  )

hex_centroids_scurve <- ggplot(
  data = hex_grid_with_counts_scurve, 
  aes(x = x, y = y)) +
  geom_polygon(color = "grey70", 
               aes(group = hex_poly_id), 
               fill = "#ffffff")  +
  geom_point(data = df_bin_centroids_scurve, 
             aes(x = c_x, y = c_y), 
             size = 1, color = "#33a02c")

hex_centroids_scurve_int <- ggplotly(hex_centroids_scurve, 
                                width = "250", 
                                height = "250", 
                                tooltip = "none") |>
  config(
    staticPlot = TRUE,        # Disables all interactivity (no hover, zoom, pan)
    displayModeBar = FALSE,   # Hides the plotly toolbar
    editable = FALSE,         # Disables annotations and editing
    showTips = FALSE,         # Removes tooltip on hover
    displaylogo = FALSE,      # Hides plotly logo
    responsive = FALSE        # Disables responsive resizing
  )

wireframe_scurve <- ggplot() +
  geom_segment(data = tr_from_to_df_scurve,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = df_bin_centroids_scurve, 
             aes(x = c_x, y = c_y), 
             size = 1, color = "#33a02c")

wireframe_scurve_int <- ggplotly(wireframe_scurve, 
                                width = "250", 
                                height = "250", 
                                tooltip = "none") |>
  config(
    staticPlot = TRUE,        # Disables all interactivity (no hover, zoom, pan)
    displayModeBar = FALSE,   # Hides the plotly toolbar
    editable = FALSE,         # Disables annotations and editing
    showTips = FALSE,         # Removes tooltip on hover
    displaylogo = FALSE,      # Hides plotly logo
    responsive = FALSE        # Disables responsive resizing
  )

>>>>

sc_xlims <- c(-0.15, 1.15)
sc_ylims <- c(-0.14, 1.05)

scurve_umap_plt <- ggplot(
  scurve_umap_scaled, 
  aes(x = emb1, y = emb2)) +
  geom_point(alpha = 0.5, color = clr_choice, size = 0.5) +
  xlim(sc_xlims) +
  ylim(sc_ylims)

scurve_umap_plt_int <- ggplotly(scurve_umap_plt, 
                                width = "350", 
                                height = "350", 
                                tooltip = "none") |>
  config(
    staticPlot = TRUE,        # Disables all interactivity (no hover, zoom, pan)
    displayModeBar = FALSE,   # Hides the plotly toolbar
    editable = FALSE,         # Disables annotations and editing
    showTips = FALSE,         # Removes tooltip on hover
    displaylogo = FALSE,      # Hides plotly logo
    responsive = FALSE        # Disables responsive resizing
  )

hex_grid_poly_scurve <- ggplot(
  data = hex_grid_with_counts_scurve, 
  aes(x = x, y = y)) +
  geom_polygon(color = "grey70", 
               aes(group = hex_poly_id), 
               fill = "#ffffff") +
  geom_point(data = scurve_umap_scaled, 
             aes(x = emb1, y = emb2), 
             alpha = 0.2, size = 0.5, color = clr_choice) + 
  xlim(sc_xlims) +
  ylim(sc_ylims)

hex_grid_poly_scurve_int <- ggplotly(hex_grid_poly_scurve, 
                                width = "350", 
                                height = "350", 
                                tooltip = "none") |>
  config(
    staticPlot = TRUE,        # Disables all interactivity (no hover, zoom, pan)
    displayModeBar = FALSE,   # Hides the plotly toolbar
    editable = FALSE,         # Disables annotations and editing
    showTips = FALSE,         # Removes tooltip on hover
    displaylogo = FALSE,      # Hides plotly logo
    responsive = FALSE        # Disables responsive resizing
  )

hex_centroids_scurve <- ggplot(
  data = hex_grid_with_counts_scurve, 
  aes(x = x, y = y)) +
  geom_polygon(color = "grey70", 
               aes(group = hex_poly_id), 
               fill = "#ffffff")  +
  geom_point(data = df_bin_centroids_scurve, 
             aes(x = c_x, y = c_y), 
             size = 1, color = "#33a02c") +
  xlim(sc_xlims) +
  ylim(sc_ylims)

hex_centroids_scurve_int <- ggplotly(hex_centroids_scurve, 
                                width = "350", 
                                height = "350", 
                                tooltip = "none") |>
  config(
    staticPlot = TRUE,        # Disables all interactivity (no hover, zoom, pan)
    displayModeBar = FALSE,   # Hides the plotly toolbar
    editable = FALSE,         # Disables annotations and editing
    showTips = FALSE,         # Removes tooltip on hover
    displaylogo = FALSE,      # Hides plotly logo
    responsive = FALSE        # Disables responsive resizing
  )

wireframe_scurve <- ggplot() +
  geom_segment(data = tr_from_to_df_scurve,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = df_bin_centroids_scurve, 
             aes(x = c_x, y = c_y), 
             size = 1, color = "#33a02c") + 
  xlim(sc_xlims) +
  ylim(sc_ylims)

wireframe_scurve_int <- ggplotly(wireframe_scurve, 
                                width = "350", 
                                height = "350", 
                                tooltip = "none") |>
  config(
    staticPlot = TRUE,        # Disables all interactivity (no hover, zoom, pan)
    displayModeBar = FALSE,   # Hides the plotly toolbar
    editable = FALSE,         # Disables annotations and editing
    showTips = FALSE,         # Removes tooltip on hover
    displaylogo = FALSE,      # Hides plotly logo
    responsive = FALSE        # Disables responsive resizing
  )
